A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add more numbers

In this section we turn our attention to the expression passed for evaluation to
\eval. \eval accepts all types of R objects as inputs. In our corpus, we observe
that \AllValueInputEvalCallPerc of all inputs to \eval are values, i.e., they evaluate to
themselves. The remaining \AllExpressionInputEvalCallPerc inputs are expressions
which are reduced to values by \eval.
% Furthermore, the proportion of values
% passed to core \eval call is \CoreEvalValueInputPerc compared to a significantly
% higher \PackageEvalValueInputPerc for package \eval calls.
To investigate this, we look at the type of expressions accepted by \eval
callsites in our corpus. We find that only \AllExpressionInputEvalSitePerc call
sites exclusively receive expressions as arguments across all program runs. The
remaining \AllPolymorphicInputEvalSitePerc call sites don't always accept expressions
as inputs. The top three of these call sites contribute to over
~80\% of all calls to evals. The first one is inside \c{match.arg} from core.
Given a vector of names as strings, this function finds the default values for
parameters with those names in the caller function. Since the default value for
a function parameter can be a complex expression or a benign value such as
\c{NULL}, \c{match.arg} evaluates it through a call to \eval. This makes the
\eval inside \c{match.arg} ``polymorhpic''. The second such \eval call
originates from the popular \ggplot package of R which is a DSL for plotting.
\ggplot has it's own object system, \ggproto, which uses \eval inside the
\ggproto function to determine the super-class from which it inherits. The
default value of the superclass is \c{NULL} but in general could be an
arbitrarily complex expression. The third \eval call is in core R \c{str}
function. This function is used to print a summary of R objects. It internally
maps \eval function on the bindings of an environment which results in inputs of
multiples types being passed to \eval.

>>>>

In this section we turn our attention to the expression passed for evaluation to
\eval. \eval accepts all types of R objects as inputs. In our corpus, we observe
that \AllValueInputEvalCallPerc of all inputs to \eval are values, i.e., they evaluate to
themselves. The remaining \AllExpressionInputEvalCallPerc inputs are expressions
which are reduced to values by \eval.
% Furthermore, the proportion of values
% passed to core \eval call is \CoreEvalValueInputPerc compared to a significantly
% higher \PackageEvalValueInputPerc for package \eval calls.
To investigate this, we look at the type of expressions accepted by \eval
callsites in our corpus. We find that only \AllValueInputEvalSitePerc receive
only values as inputs, \AllExpressionInputEvalSitePerc call
sites exclusively receive expressions as inputs and a very large proportion,
\AllPolymorphicInputEvalSitePerc, receive both expressions and values as inputs across all program runs.
We inspected the eval callsites that accept only values or both values and expression as inputs.
The top three of these call sites contribute to over
~80\% of all calls to evals. The first one is inside \c{match.arg} from core.
Given a vector of names as strings, this function finds the default values for
parameters with those names in the caller function. Since the default value for
a function parameter can be a complex expression or a benign value such as
\c{NULL}, \c{match.arg} evaluates it through a call to \eval. This makes the
\eval inside \c{match.arg} ``polymorhpic''. The second such \eval call
originates from the popular \ggplot package of R which is a DSL for plotting.
\ggplot has it's own object system, \ggproto, which uses \eval inside the
\ggproto function to determine the super-class from which it inherits. The
default value of the superclass is \c{NULL} but in general could be an
arbitrarily complex expression. The third \eval call is in core R \c{str}
function. This function is used to print a summary of R objects. It internally
maps \eval function on the bindings of an environment which results in inputs of
multiples types being passed to \eval.
